Windowed least-squares model reduction for dynamical systems

### 2019-10-16 section4/spatial_numerical.tex
fix error

%where 
%\begin{align*}
%\residArg{n,i} &: (\stateyArgnt{n,i},\ldots,\stateyArgnt{n,i-k(i)}) \mapsto  \sum_{j=0}^k \alpha_j \stateyArgnt{n,i-j} = \Delta t^{n,i} \sum_{j=0}^k \beta_j \velocity(\stateyArgnt{n,i-j}),
%\\
%               &: \RR{\fomdim} \otimes \RR{k(i)} \rightarrow \RR{\fomdim}, 
%\end{align*} 
%is the discrete residual resulting from the linear multistep scheme and 
%\methodAcronym\ solves the minimization problem over each time window, 
%\begin{align*}
%&\approxstateDiscreteArg{n,0},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}} = \underset{\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}} \in \trialspace}{\text{arg\,min } }
%\objectiveArgLMS{n} (\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}}) \\
%& \text{subject to} \hspace{0.2 in}  \approxstateDiscreteArg{n,0} =
%\begin{cases} \approxstateDiscreteArg{n-1,\nstepsArg{n-1}} & n = 2,\ldots,\nslabs,\\
%\approxstateIC & n=1. \end{cases} \end{align*}
	Equivalently, \methodAcronym\ sequentially computes the generalized
	coordinates
	$\genstateDiscreteArg{n,1},\ldots,\genstateDiscreteArg{n,\timeWindowArg{n}{i}}$,
	$n=1,\ldots,\nslabs$ 
with $\genstateDiscreteArg{n,i}(\approx
	\genstateArgnt{n}(\timeWindowArg{n}{i}))\in\RR{\romdim}$
	that satisfy
\begin{equation}\label{eq:obj_gen_lms_final}
\begin{split}
	&
	\underset{(\genstateyDiscreteArg{1},\ldots,\genstateyDiscreteArg{\nstepsArg{n}})\in\RR{\romdimArg{n}}\otimes \RR{\nstepsArg{n}}}{\text{minimize } }
\objectiveArgLMS{n} (\basisspaceArg{n} \genstateyDiscreteArg{1} + \stateInterceptArg{n},\ldots,\basisspaceArg{n} \genstateyDiscreteArg{\nstepsArg{n}} + \stateInterceptArg{n}). 
%& \text{subject to} \hspace{0.2 in}
%\genstateyDiscreteArg{0} =
%\begin{cases} \genspatialICDiscrete  & n = 2,\ldots,\nslabs \\
%\genstateICOne& n=1. \end{cases} 
\end{split}
\end{equation}
%\begin{equation}\label{eq:obj_gen_lms_final}
%\begin{split}
%& \genstateDiscreteArg{n,0},\ldots,\genstateDiscreteArg{n,\nstepsArg{n}}  = \underset{\genstateyDiscreteArg{n,0},\ldots,\genstateyDiscreteArg{n,\nstepsArg{n}}}{\text{arg\,min } }
%\objectiveArgLMS{n} (\basisspace \genstateyDiscreteArg{n,0} + \stateIntercept,\ldots,\basisspace \genstateyDiscreteArg{n,\nstepsArg{n}} + \stateIntercept) \\ 
%& \text{subject to} \hspace{0.2 in}
%\genstateDiscreteArg{n,0} =
%\begin{cases} \genstateDiscreteArg{n-1, \nstepsArg{n-1}} & n = 2,\ldots,\nslabs \\
%\basisspace^T(\stateFOMIC - \stateIntercept)& n=1. \end{cases} 
%\end{split}
%\end{equation}
The optimization problem takes the form of a \textit{weighted least-squares
	problem}. 
We emphasize that optimization problem~\eqref{eq:obj_gen_lms_final} associates
	with an \spatialAcronym\ trial subspace characterized by a reduction in
	spatial complexity, but no reduction in temporal complexity.

>>>>

%where 
%\begin{align*}
%\residArg{n,i} &: (\stateyArgnt{n,i},\ldots,\stateyArgnt{n,i-k(i)}) \mapsto  \sum_{j=0}^k \alpha_j \stateyArgnt{n,i-j} = \Delta t^{n,i} \sum_{j=0}^k \beta_j \velocity(\stateyArgnt{n,i-j}),
%\\
%               &: \RR{\fomdim} \otimes \RR{k(i)} \rightarrow \RR{\fomdim}, 
%\end{align*} 
%is the discrete residual resulting from the linear multistep scheme and 
%\methodAcronym\ solves the minimization problem over each time window, 
%\begin{align*}
%&\approxstateDiscreteArg{n,0},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}} = \underset{\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}} \in \trialspace}{\text{arg\,min } }
%\objectiveArgLMS{n} (\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}}) \\
%& \text{subject to} \hspace{0.2 in}  \approxstateDiscreteArg{n,0} =
%\begin{cases} \approxstateDiscreteArg{n-1,\nstepsArg{n-1}} & n = 2,\ldots,\nslabs,\\
%\approxstateIC & n=1. \end{cases} \end{align*}
	Equivalently, \methodAcronym\ sequentially computes the generalized
	coordinates
	$\genstateDiscreteArg{n,1},\ldots,\genstateDiscreteArg{n,\nstepsArg{n}}$,
	$n=1,\ldots,\nslabs$ 
with $\genstateDiscreteArg{n,i}(\approx
	\genstateArgnt{n}(\timeWindowArg{n}{i}))\in\RR{\romdim}$
	that satisfy
\begin{equation}\label{eq:obj_gen_lms_final}
\begin{split}
	&
	\underset{(\genstateyDiscreteArg{1},\ldots,\genstateyDiscreteArg{\nstepsArg{n}})\in\RR{\romdimArg{n}}\otimes \RR{\nstepsArg{n}}}{\text{minimize } }
\objectiveArgLMS{n} (\basisspaceArg{n} \genstateyDiscreteArg{1} + \stateInterceptArg{n},\ldots,\basisspaceArg{n} \genstateyDiscreteArg{\nstepsArg{n}} + \stateInterceptArg{n}). 
%& \text{subject to} \hspace{0.2 in}
%\genstateyDiscreteArg{0} =
%\begin{cases} \genspatialICDiscrete  & n = 2,\ldots,\nslabs \\
%\genstateICOne& n=1. \end{cases} 
\end{split}
\end{equation}
%\begin{equation}\label{eq:obj_gen_lms_final}
%\begin{split}
%& \genstateDiscreteArg{n,0},\ldots,\genstateDiscreteArg{n,\nstepsArg{n}}  = \underset{\genstateyDiscreteArg{n,0},\ldots,\genstateyDiscreteArg{n,\nstepsArg{n}}}{\text{arg\,min } }
%\objectiveArgLMS{n} (\basisspace \genstateyDiscreteArg{n,0} + \stateIntercept,\ldots,\basisspace \genstateyDiscreteArg{n,\nstepsArg{n}} + \stateIntercept) \\ 
%& \text{subject to} \hspace{0.2 in}
%\genstateDiscreteArg{n,0} =
%\begin{cases} \genstateDiscreteArg{n-1, \nstepsArg{n-1}} & n = 2,\ldots,\nslabs \\
%\basisspace^T(\stateFOMIC - \stateIntercept)& n=1. \end{cases} 
%\end{split}
%\end{equation}
The optimization problem takes the form of a \textit{weighted least-squares
	problem}. 
We emphasize that optimization problem~\eqref{eq:obj_gen_lms_final} associates
	with an \spatialAcronym\ trial subspace characterized by a reduction in
	spatial complexity, but no reduction in temporal complexity.
